Finding R Local R Authors
=========================

As I'm organizing [my local R users' group](http://www.noamross.net/davis-r-users-group.html), I got interested in learning who at UC Davis was active in the R community.  One thought I had was to look up what R packages were written by people at UC Davis, so I wrote a function to look this up in CRAN:

```{r}
require(balleRs)
search_in_CRAN_packages
```

The function takes a vector of strings and returns a nicely formatted table (in pandoc format, thanks to the `pander` package) of packages and the fields that contain those strings.  to search for local authors, I search for my school name and its domain:

```{r results='asis'}
search_in_CRAN_packages(c("UC Davis", "ucdavis.edu"))
```

I've put this function as the start of a package called "balleRs" on github.  I want to add a bunch of other tools to find poweR users on the web, such as scraping the R-help archives, Stack Overflow, and Cross-Validated.  Next: Bioconductor authors!

